Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-06 doc/manuscript/manuscript.Rmd
Add compound DAPC figure to paper

## DAPC analysis {-}

>>>>

## DAPC {-}

![
Discriminant Analysis on regions showing that Mexico is differentiated from other populations. 
**(a)** Mean population assignment (horizontal axis) probability (vertical axis) for all populations with N > 10 (facets).
All values sum to one.
**(b)** Scatter plot of first two components from DAPC.
Points represent observed individuals connected to the population centroids with ellipses representing a 66% confidence interval for a normal distribution. 
](../../results/figures/publication/DAPC.pdf){#DAPC width=100%}
